### 2019-03-13 assignments/5/Assignment_5.Rmd
Did Assignment 5.4

3
F84 is not available in raxml, so I'm using F81
Raxml: Final LogLikelihood -54568.308901
FastMe: Final LogLikelihood -54674.432495

4

>>>>

## 3
F84 is not available in raxml, so I'm using F81.
The trees are not the same (see following tanglegram), they also have different log-likelihood scores:

```
Raxml:  -54568.308901
FastMe: -54674.432495
```
![Tanglegram made with Dendroscope](3/Tanglegram.png)

## 4
These are the two commands I used:

```
raxml-ng --search --msa ../alignment.phy --model model_codons --prefix codons --seed 12 --brlen scaled
raxml-ng --search --msa ../alignment.phy --model model_genes --prefix genes --seed 12 --brlen scaled
```

The two models looked like this:

````
model_codons:
  GTR+G+FO, COBX=1-4482/3

model_genes:
  GTR+G+FO, cob=1-1248
  GTR+G+FO, cox1=1249-2808
  GTR+G+FO, cox2=2809-3543
  GTR+G+FO, cox3=3544-4482
```

These are the log-likelihoods for the best tree:

```
Codons: -45373.634679
Genes:  -45270.430490
```

They are much better than the original tree BUT the evolution models I used are different so I'm not sure if it's directly comparable.

Anyway, here is the difference between the Gene partitioned tree and the original RaXML tree, they are very similar except for the rabbit:

![Tanglegram made with Dendroscope](4/Genes_vs_3_raxml.png)

## 5
Unfortunately I can't do this part right now because HPC is having problems with slurm or something (I copied you on an email about this). I will resubmit this assignment including this part when it's fixed.
